Semi-Inclusive Deep Inelastic Scattering in Wandzura-Wilczek-type approximation

### 2018-01-09 tex/test-WW-type-00s-PS.tex
alexei

Retaining the only non-zero term in the WW-type approximation, and
assuming for $h_L^q(x,\kperp)$ a Gaussian Ansatz, we obtain
for the structure function 
\begin{subequations}\ba
	F_{UL}^{\sin\phi_h}(x,z,\Phperp) 
	&=& \frac{2M}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\; 
	b^{(1)}_{\rm A}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \, , \\
	F_{UL}^{\sin\phi_h}(x,z,\la\Phperp\ra) 
	&=& \frac{2M}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\;  
	c^{(1)}_{\rm A}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{h_L} + \avpperp_{H_1^\perp}$ and
$b^{(1)}_{\rm A}=2m_h$ and $c^{(1)}_{\rm A} = \sqrt{\pi}\,m_h$,
see App.~\ref{App:convol-details} for details. We now approximate 
$\avkperp_{h_L}=\avkperp_{h_1}$ and explore (\ref{Eq:WW-type-6}) to estimate
\be
	xh_L^q(x) = h_{1L}^{\perp(1)q}(x)
\ee
and finally express $h_{1L}^{\perp(1)q}(x)$ in terms of $h_1^a(x)$
using (\ref{Eq:WW-approx-h1L}). $h_{1L}^{\perp(1)q}(x)$  is shown in Fig.~\ref{g1t_h1l_functions}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_COMPASS_x.pdf} (a)
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf} (b)
\caption{\label{aulsinphi_jlab} $A_{UL}^{\sin\phi_h}$  as a function of $ x $  for COMPASS (a), and  comparison to HERMES data \cite{Airapetian:2005jc} (b).
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Retaining the only non-zero term in the WW-type approximation, and
assuming for $g_T^{\perp a}(x,\kperp)$ a Gaussian Ansatz, we obtain
for the structure function 
\begin{subequations}\ba
	F_{LT}^{\cos(2\phi_h - \phi_S)}(x,z,\Phperp) 
	&=& \red{-}x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\; 
	b^{(2)}_{C}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!2}\,
	{ \cal G}(\Phperp)\, , \\
	F_{LT}^{\cos(2\phi_h - \phi_S)}(x,z,\la\Phperp\ra) 
	&=& \red{-}x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\;  
	c^{(2)}_{C}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{\!2}\,
	\label{eq:asymmetry_auu_cos2phi}
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{g_{T}^\perp} + \avpperp_{D_1}$ and 
$b^{(2)}_{\rm C}=c^{(2)}_{\rm C} = M_N^2$, 
see App.~\ref{App:convol-details} for details. 
We estimate $\avkperp_{g_{T}^\perp}=\avkperp_{g_1}$ and explore
the WW-type approximation (\ref{Eq:WW-type-gTperp}), 
\be
	xg_T^{\perp(2)q}(x) = \frac{\la\kperp^2\ra_{g_{1T}^\perp}}{M_N^2}\;
	g_{1T}^{\perp (1)q}(x)\,,
\ee
where we finally express $g_{1T}^{\perp (1)q}(x)$ in terms of $g_1^q(x)$ 
according to Eq.~(\ref{Eq:WW-approx-g1T}).

The asymmetry  $A_{LT}^{\cos(\phi_h -\phi_S)}=F_{LT}^{\cos(\phi_h -\phi_S)}/F_{UU}$ 
as a function of $x$ and $P_{hT}$ for Jefferson Lab 12 GeV is plotted in 
Fig.~\ref{altcos2phi_jlab}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/ALTcos2phi_x.pdf} 
\includegraphics[width=0.45\textwidth]{\FigPath/ALTcos2phi_PT.pdf}
\caption{\label{altcos2phi_jlab} $A_{LT}^{\cos(2\phi_h - \phi_S)}$  as a function of $ x $ (left panel), and   as a function of $P_{hT}$ (right panel) at typical kinematics of Jefferson Lab 12 GeV, $\la x\ra = 0.25$, $\la z\ra = 0.54$, $\la Q^2\ra = 2.4$ GeV$^2$.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

Retaining the only non-zero term in the WW-type approximation, and
assuming for $h_L^q(x,\kperp)$ a Gaussian Ansatz 
\be
h_L^q(x,\kperp^2) = h_L^q(x) \,\frac{1}{\pi \avkperp_{h_{L}}}\,
	e^{-\kperp^2/{\avkperp_{h_{L}}}}\;,
	\label{eq:hLnew}
\ee
we obtain
for the structure function 
\begin{subequations}\ba
	F_{UL}^{\sin\phi_h}(x,z,\Phperp) 
	&=& \frac{2M}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\; 
	b^{(1)}_{\rm A}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)\,
	{ \cal G}(\Phperp ) \, , \\
	F_{UL}^{\sin\phi_h}(x,z,\la\Phperp\ra) 
	&=& \frac{2M}{Q}\,x\sum_q e_q^2\,x\,h_{L}^{q}(x)\,H_1^{\perp(1)q}(z)\;  
	c^{(1)}_{\rm A}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)\,
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{h_L} + \avpperp_{H_1^\perp}$ and
$b^{(1)}_{\rm A}=2m_h$ and $c^{(1)}_{\rm A} = \sqrt{\pi}\,m_h$,
see App.~\ref{App:convol-details} for details. We now approximate 
$\avkperp_{h_L}=\avkperp_{h_1}$ and explore (\ref{Eq:WW-type-6}) to estimate
\be
	xh_L^q(x) = -2 h_{1L}^{\perp(1)q}(x)
\ee
and finally express $h_{1L}^{\perp(1)q}(x)$ in terms of $h_1^a(x)$
using (\ref{Eq:WW-approx-h1L}). $h_{1L}^{\perp(1)q}(x)$  is shown in Fig.~\ref{g1t_h1l_functions}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_HERMES_x.pdf} (a)
\includegraphics[width=0.45\textwidth]{\FigPath/AULsinphi_COMPASS_x.pdf} (b)
\caption{\label{aulsinphi_jlab} $A_{UL}^{\sin\phi_h}$  as a function of $ x $ , comparison to HERMES data \cite{Airapetian:2005jc} (a), and predictions for COMPASS (b).
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Retaining the only non-zero term in the WW-type approximation, and
assuming for $g_T^{\perp a}(x,\kperp)$ a Gaussian Ansatz
\be
	g^{\perp q}_{T}(x,\kperp^2) = 
	g^{\perp (2) q}_{T}(x)\,\frac{2 M^4}{\pi \avkperp^3_{g_{T}^{\perp} }}\,
	e^{-\kperp^2/{\avkperp_{g_{T}^{\perp} }}}\;,
	\label{eq:gtperpnew}
\ee
We estimate $\avkperp_{g_{T}^\perp}=\avkperp_{g_1}$ and explore
the WW-type approximation (\ref{Eq:WW-type-gTperp}), 
\be
	xg_T^{\perp(2)q}(x) = \frac{\la\kperp^2\ra_{g_{1T}^\perp}}{M_N^2}\;
	g_{1T}^{\perp (1)q}(x)\,,
\ee
where we finally express $g_{1T}^{\perp (1)q}(x)$ in terms of $g_1^q(x)$ 
according to Eq.~(\ref{Eq:WW-approx-g1T}).

We obtain
for the structure function 
\begin{subequations}\ba
	F_{LT}^{\cos(2\phi_h - \phi_S)}(x,z,\Phperp) 
	&=& -\frac{2M}{Q} x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\; 
	b^{(2)}_{C}\,\biggl(\frac{z \Phperp} {\lambda}\biggr)^{\!2}\,
	{ \cal G}(\Phperp)\, , \\
	F_{LT}^{\cos(2\phi_h - \phi_S)}(x,z,\la\Phperp\ra) 
	&=& -\frac{2M}{Q} x \sum_q e_q^2\,x\,g_{T}^{\perp (2) q}(x)\,D_1^q(z)\;  
	c^{(2)}_{C}\,\biggl(\frac{z} {\lambda^{1/2}}\biggr)^{\!2}\,
	\label{eq:asymmetry_auu_cos2phi}
\ea\end{subequations}
where $\lambda=z^2 \avkperp_{g_{T}^\perp} + \avpperp_{D_1}$ and 
$b^{(2)}_{\rm C}=c^{(2)}_{\rm C} = M_N^2$, 
see App.~\ref{App:convol-details} for details.

The asymmetry  $A_{LT}^{\cos(\phi_h -\phi_S)}=F_{LT}^{\cos(\phi_h -\phi_S)}/F_{UU}$ 
as a function of $x$ and $P_{hT}$ for COMPASS is plotted in 
Fig.~\ref{altcos2phi_jlab}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[ht]
\centering
\includegraphics[width=0.45\textwidth]{\FigPath/ALTcos2PhiminusPhiS_COMPASS_x.pdf} 
\caption{\label{altcos2phi_jlab} $A_{LT}^{\cos(2\phi_h - \phi_S)}$  as a function of $ x $ for COMPASS.
}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
